\documentclass[a4paper,12pt]{amsart}

\input{preambles.tex}

\begin{document}

% Top matter
\title[Project Plan]{Project Plan for the Course COMP1110 -- Group D08}
% Authors, in alphabetical order by surname
%%
\newcommand{\cBanh}{C. Banh}
\author[\cBanh]{Chun Hei Banh}
\address{\cBanh, BEng(Elite/AI\&DataSc), 3036570233, \href{mailto:kbch@connect.hku.hk}{\texttt{kbch@connect.hku.hk}}}
%
\newcommand{\sLiu}{S. Liu}
\author[\sLiu]{Sze Pok Liu}
\address{\sLiu, BEng(AI\&DataSc), 3036589454, \href{mailto:u3658945@connect.hku.hk}{\texttt{u3658945@connect.hku.hk}}}
%
\newcommand{\jShing}{J. Shing}
\author[\jShing]{Zhan Ho Jacob Shing}
\address{\jShing, BEng(CompSc), 3036228892, \href{mailto:jacobszh@connect.hku.hk}{\texttt{jacobszh@connect.hku.hk}}}
%
\newcommand{\yYe}{Y. Ye}
\author[\yYe]{Yubing Ye}
\address{\yYe, BEng(CompSc), 3036291502, \href{mailto:u3629150@connect.hku.hk}{\texttt{u3629150@connect.hku.hk}}}
%
\newcommand{\yZhang}{Y. Zhang}
\author[\yZhang]{Yikun Zhang}
\address{\yZhang, BEng(CompSc), 3036482333, \href{mailto:pzdmmsd@connect.hku.hk}{\texttt{pzdmmsd@connect.hku.hk}}}
%%
\date{21 March 2026}
\maketitle

% BODY

\section{Topic Selection \& Introduction}

The group has selected the topic \textbf{B. Smart Public Transport Advisor} for the project.
For the project, the group will implement a route planner with the focus for pedestrian navigation within the campus of The University of Hong Kong (HKU).
To achieve that, the group will model the campus as an undirected multigraph as defined mathematically by:
\begin{equation} \label{eq:graph}
    G=(V,E),
\end{equation}
where for each vertex $v \in V$, $v$ represents a key location on the campus, such as a building entrance, a canteen, etc.;
and for each edge $e \in E$ represents an undirected path between two distinct vertices.
In addition to the graph structure, each edge will have a set of attributes, such as the average walking time, type of path (e.g., slope, stairs, etc.), etc.
The details of what attributes to include will be determined during the design phase of the project.

\section{Review of Existing Solutions}

For researching purposes, the group will review three types of existing solutions, each with two examples:
\begin{enumerate}
    \item \textbf{General purpose route planners}: Google Maps, Citymapper;
    \item \textbf{Transportation-specific route planners}: MTR Mobile App, HKBUS.app; and
    \item \textbf{Static navigation systems}: HKU campus map, On-campus navigation signages.
\end{enumerate}
The examples will be evaluated across several dimensions, such as easiness of use, specificity for pedestrian navigation, etc.
The conclusions drawn from the comparison shall be used to fine-tune the design of our own route planning implementation.

\section{Task Decomposition, Assignments \& Timeline}

The project will be decomposed into three phases: \textbf{Research \& Design}, \textbf{Implementation}, and \textbf{Case Study, Test, \& Evaluation}, each with its dedicated tasks.
Each task has a defined timeline and expected deliverables, which will be detailed in the following subsections.

\subsection{Task decomposition}
The tasks, along with their descriptions, expected deliverables, and time estimates, are listed in Table~\ref{tab:tasks}.

\begin{landscape}
\begin{longtable}{c >{\raggedright\arraybackslash}m{4cm} >{\raggedright\arraybackslash}m{8cm} >{\raggedright\arraybackslash}m{8cm} >{\centering\arraybackslash}m{1.2cm}}
    % --- Head (first page only) ---
    \caption{A list of tasks for accomplishing the project, along with their descriptions, expected deliverables, and time estimations.}
    \label{tab:tasks}\\
    \toprule
    \textbf{Task ID} & \textbf{Phase} & \textbf{Description} & \textbf{Expected Deliverables} & \textbf{Time (days)} \\
    \midrule
    \endfirsthead
    % --- End of Head (first page) ---

    % --- Head (subsequent pages) ---
    \multicolumn{5}{c}{Table\ \thetable. \textit{Continued from last page.}} \\[1em]
    \toprule
    \textbf{Task ID} & \textbf{Phase} & \textbf{Description} & \textbf{Expected Deliverables} & \textbf{Time (days)} \\
    \midrule
    \endhead
    % --- End of Head (subsequent pages) ---

    % --- Foot (all pages except the last one) ---
    \multicolumn{5}{r}{\textit{Continued on next page.}} \\
    \endfoot
    % --- End of Foot (all pages except the last one) ---

    % --- Foot (last page) ---
    \bottomrule
    \endlastfoot
    % --- End of Foot (last page) ---

    % --- Body (all pages) ---
    \hypertarget{task:r01}{\texttt{R01}} & Research \& Design & Survey existing navigation solutions and compare them in a table format. & Comparison table of existing tools (target users, key features, missing features, etc.) with summary takeaways. & 3 \\
    \midrule[0.2pt]
    \hypertarget{task:r02}{\texttt{R02}} & Research \& Design & Problem modeling for our solution: define core entities, input/output, and coverage scope. & Documentation of core concepts (stop, segment, journey, etc.), input/output specifications, scope of coverage. & 1 \\
    \midrule[0.2pt]
    \hypertarget{task:i01}{\texttt{I01}} & Implementation & Data collection: assign responsible areas to each team member, measure and record paths between designated nodes. & Collected path data (distance, time, cost, etc.), raw measurement records or data sheets. & 7 \\
    \midrule[0.2pt]
    \hypertarget{task:i02}{\texttt{I02}} & Implementation & Coding: basic data structures in Python. & Implemented data structure classes (e.g., Graph, Node, Edge) with methods for serialization, deserialization, and basic operations. & 3 \\
    \midrule[0.2pt]
    \hypertarget{task:i03}{\texttt{I03}} & Implementation & Coding: text-based application UI with main functionality for selecting origin/destination and preferences. & A text-based user interface (based on \texttt{Textual}) for user to choose origin/destination and preferences, with backend integration for route planning. & 10 \\
    \midrule[0.2pt]
    \hypertarget{task:i03a}{\texttt{I03A}} & Implementation & Coding: data management UI for interactive data collection and editing. & (Optional) Interactive data management tool supporting CRUD operations on data. & 5 \\
    \midrule[0.2pt]
    \hypertarget{task:i04}{\texttt{I04}} & Implementation & Coding: route search logic (candidate generation, scoring, ranking). & Route search algorithm code, find the optimal itinerary based on the user's selected preferences (such as cost, duration, number of segments). & 5 \\
    \midrule[0.2pt]
    \hypertarget{task:i05}{\texttt{I05}} & Implementation & Coding: advanced preference mode. & An algorithm that can avoid stairs, or pick routes that are accessibility-focused, etc. & 3 \\
    \midrule[0.2pt]
    \hypertarget{task:c01}{\texttt{C01}} & Case Study, Test, \& Evaluation & Scenario design: write 3 to 4 user scenarios with goals, network layout, origin/destination, and preference modes. & Document describing 3 to 4 user scenarios. & 2 \\
    \midrule[0.2pt]
    \hypertarget{task:c02}{\texttt{C02}} & Case Study, Test, \& Evaluation & Record input/output for scenarios. Run the program for each scenario and capture results. & Input parameters and program outputs for each scenario. & 1 \\
    \midrule[0.2pt]
    \hypertarget{task:c03}{\texttt{C03}} & Case Study, Test, \& Evaluation & Analyze the competence of our solution and compare with existing solutions. & Analysis report on solution capabilities, comparison with existing tools. & 2 \\
    \midrule[0.2pt]
    \hypertarget{task:c04}{\texttt{C04}} & Case Study, Test, \& Evaluation & Discussion and suggestions: summarize strengths, limitations, and future improvements. & Discussion document with limitations analysis and improvement directions. & 2 \\
\end{longtable}
\end{landscape}

\subsection{Task assignments}
The task assignments are listed in Table~\ref{tab:task-assignments}.

\begin{table}
    \caption{The tasks as defined in Table~\ref{tab:tasks} and their assignees. Asterisk (\texttt{*}) indicates the person has been assigned to the task.}\label{tab:task-assignments}
    \begin{tabular}{cccccc}
        \toprule
        \diagbox{\textbf{Task ID}}{\textbf{Assignee}} & \textbf{\cBanh} & \textbf{\sLiu} & \textbf{\jShing} & \textbf{\yYe} & \textbf{\yZhang} \\
        \midrule
        \hyperlink{task:r01}{\texttt{R01}}      & \texttt{*}    & \texttt{*}    &               &               &               \\
        \hyperlink{task:r02}{\texttt{R02}}      &               & \texttt{*}    & \texttt{*}    &               & \texttt{*}    \\ \midrule[0.2pt]
        \hyperlink{task:i01}{\texttt{I01}}      & \texttt{*}    &               & \texttt{*}    & \texttt{*}    & \texttt{*}    \\
        \hyperlink{task:i02}{\texttt{I02}}      & \texttt{*}    &               & \texttt{*}    & \texttt{*}    & \texttt{*}    \\
        \hyperlink{task:i03}{\texttt{I03}}      & \texttt{*}    &               & \texttt{*}    & \texttt{*}    & \texttt{*}    \\
        \hyperlink{task:i03a}{\texttt{I03A}}    & \texttt{*}    &               & \texttt{*}    & \texttt{*}    & \texttt{*}    \\
        \hyperlink{task:i04}{\texttt{I04}}      & \texttt{*}    &               & \texttt{*}    & \texttt{*}    & \texttt{*}    \\
        \hyperlink{task:i05}{\texttt{I05}}      & \texttt{*}    &               & \texttt{*}    & \texttt{*}    & \texttt{*}    \\ \midrule[0.2pt]
        \hyperlink{task:c01}{\texttt{C01}}      &               & \texttt{*}    &               & \texttt{*}    &               \\
        \hyperlink{task:c02}{\texttt{C02}}      & \texttt{*}    & \texttt{*}    &               & \texttt{*}    &               \\
        \hyperlink{task:c03}{\texttt{C03}}      & \texttt{*}    & \texttt{*}    &               &               &               \\
        \hyperlink{task:c04}{\texttt{C04}}      & \texttt{*}    & \texttt{*}    &               &               &               \\
        \bottomrule
    \end{tabular}
\end{table}

\subsection{Plan timeline}
Note that the tasks set out in Table~\ref{tab:tasks} are not necessarily executed sequentially and linearly.
They may be arranged in parallel where possible and appropriate.
The timeline for the project and the dependency of tasks are illustrated by the Gantt chart in Figure~\ref{fig:project-gantt-chart}.

The timeline is merely a rough estimation and may be adjusted as the project progresses.
There is a buffer period at the end of the project to accommodate any unforeseen delays or additional work that may arise during the project execution.

\begin{landscape}
\begin{figure}
    \begin{ganttchart}
        [
            time slot format=little-endian,
            expand chart=\linewidth,
            title height=1,
            y unit title=0.6cm,
            y unit chart=0.8cm,
            hgrid=true,
            vgrid=true,
            bar height=0.8,
            bar top shift=0.1,
            group top shift=0.6,
            bar label font=\color{black}\footnotesize,
            group label font=\bfseries\footnotesize,
            group left shift=0,
            group right shift=0,
            group left peak tip position=0,
            group left peak width=0.2,
            group right peak tip position=0,
            group right peak width=0.2,
        ]
        {24-03-2026}{30-04-2026}
        % Title
        \gantttitle{\bfseries Project Timeline}{38} \\
        \gantttitlecalendar[title label font=\footnotesize]{month=shortname, day}
        \ganttnewline
        % Tasks
        % Task Phase R
        \ganttgroup[
            group/.append style={draw=blue!70!black, fill=blue!60}
        ]{\color{blue!70!black} Research \& Design}{24-03-2026}{26-03-2026} \\
        \ganttbar[
            name=tr01,
            bar/.append style={draw=blue!70!black, fill=blue!20, fill opacity=0.45}
        ]{\texttt{R01} -- Survey}{24-03-2026}{26-03-2026} \\
        \ganttbar[
            name=tr02,
            bar/.append style={draw=blue!70!black, fill=blue!20, fill opacity=0.45}
        ]{\texttt{R02} -- Design}{24-03-2026}{26-03-2026} \\
        % Task Phase I
        \ganttgroup[
            group/.append style={draw=teal!70!black, fill=teal!65}
        ]{\color{teal!70!black} Implementation}{28-03-2026}{10-04-2026} \\
        \ganttbar[
            name=ti01,
            bar/.append style={draw=teal!70!black, fill=teal!18, fill opacity=0.45}
        ]{\texttt{I01} -- Data collection}{28-03-2026}{03-04-2026} \\
        \ganttlink{tr02}{ti01}
        \ganttlink{tr01}{ti01}
        \ganttbar[
            name=ti02,
            bar/.append style={draw=teal!70!black, fill=teal!18, fill opacity=0.45}
        ]{\texttt{I02} -- Write data classes}{28-03-2026}{30-03-2026} \\
        \ganttlink{tr02}{ti02}
        \ganttlinkedbar[
            name=ti03a,
            bar/.append style={draw=teal!70!black, fill=teal!18, fill opacity=0.45}
        ]{\texttt{I03A} -- Write data management UI}{01-04-2026}{05-04-2026} \\
        \ganttbar[
            name=ti03,
            bar/.append style={draw=teal!70!black, fill=teal!18, fill opacity=0.45}
        ]{\texttt{I03} -- Write text UI}{01-04-2026}{10-04-2026} \\
        \ganttlink{ti02}{ti03}
        \ganttbar[
            name=ti04,
            bar/.append style={draw=teal!70!black, fill=teal!18, fill opacity=0.45}
        ]{\texttt{I04} -- Write route search logic}{04-04-2026}{08-04-2026} \\
        \ganttlink{ti01}{ti04}
        \ganttlinkedbar[
            name=ti05,
            bar/.append style={draw=teal!70!black, fill=teal!18, fill opacity=0.45}
        ]{\texttt{I05} -- Write advanced preference mode}{09-04-2026}{11-04-2026} \\
        % Task Phase C
        \ganttgroup[
            group/.append style={draw=orange!80!black, fill=orange!70}
        ]{\color{orange!80!black} Case Study, Test, \& Evaluation}{13-04-2026}{19-04-2026} \\
        \ganttbar[
            name=tc01,
            bar/.append style={draw=orange!80!black, fill=orange!22, fill opacity=0.45}
        ]{\texttt{C01} -- Scenario design}{13-04-2026}{14-04-2026} \\
        \ganttlink{ti03}{tc01}
        \ganttlink{ti04}{tc01}
        \ganttlink{ti05}{tc01}
        \ganttlinkedbar[
            name=tc02,
            bar/.append style={draw=orange!80!black, fill=orange!22, fill opacity=0.45}
        ]{\texttt{C02} -- Run scenarios and record results}{15-04-2026}{15-04-2026} \\
        \ganttlinkedbar[
            name=tc03,
            bar/.append style={draw=orange!80!black, fill=orange!22, fill opacity=0.45}
        ]{\texttt{C03} -- Analyze solution capabilities}{16-04-2026}{17-04-2026} \\
        \ganttlinkedbar[
            name=tc04,
            bar/.append style={draw=orange!80!black, fill=orange!22, fill opacity=0.45}
        ]{\texttt{C04} -- Discussion and suggestions}{18-04-2026}{19-04-2026} \\
        % Buffer bar
        \ganttbar[
            name=buffer,
            bar/.append style={draw=none, fill=black!65, fill opacity=0.30}
        ]{\textit{\color{black!65} Buffer}}{20-04-2026}{30-04-2026}
    \end{ganttchart}
    \caption{The Gantt chart illustrating the project execution.}\label{fig:project-gantt-chart}
\end{figure}
\end{landscape}

\end{document}
